Pillar 1 - Sequential Pattern Mining

### 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd

  # Identifying item
  mutate(
    item_G = paste(item, Grade_round, sep = "_")
    )
```

### Preceding courses
```{r}
d_cumulative_transcript <-  d_transactions        %>%
  select(sequenceID, item, eventID)  %>%
  arrange(sequenceID, eventID, item) %>%
  group_by(sequenceID, eventID)      %>%
  summarize_all(paste, collapse=" ") %>%
  arrange(sequenceID, eventID)       %>%
  mutate(
    course_all  = paste(unique(d_transactions$item), collapse = " "),
    course_all  = str_split(course_all, pattern = " "),

@@

### Computing Support
```{r}

>>>>

  # Identifying item
  mutate(
    item_G = paste(item, Grade_round, sep = "_")
    )
```
### Additional General Dataframes for courses
#### Transcript with Preceding courses per student
```{r}
d_cumulative_transcript <-  d_transactions        %>%
  select(sequenceID, item, eventID)  %>%
  arrange(sequenceID, eventID, item) %>%
  group_by(sequenceID, eventID)      %>%
  summarize_all(paste, collapse=" ") %>%
  arrange(sequenceID, eventID)       %>%
  mutate(
    course_all  = paste(unique(d_transactions$item), collapse = " "),
    course_all  = str_split(course_all, pattern = " "),

@@

#### Courses that were taken before each course
```{r}
d_past_student_course <- d_cumulative_transcript %>%
  select(sequenceID, eventID, item, course_past)%>%
  unnest(item, .drop=F)

d_past_course <- expand.grid(

  # Expand along students (sequenceID) and courses (itemID)
  sequenceID = unique(d_transactions$sequenceID),
  item       = unique(d_transactions$item),
  stringsAsFactors = FALSE
  ) %>%
  full_join(d_past_student_course, by= c("sequenceID", "item")) %>%  #ATTENTION: Duplicates resits. Adds values per retake of course (eg.10177849 SCI3048)
  arrange(sequenceID) %>%
  ungroup() %>%
  drop_na(eventID) %>%
  unnest(course_past) %>%
  distinct() %>%
  group_by(item) %>%
  summarise(full_past = paste( course_past, collapse = " ")) %>% #difference, between this and above?
  mutate(full_past    = str_split(full_past, pattern = " "),
         full_past    = map(.f= unique, .x=full_past),
         total_past_courses = map(.f=length, .x=full_past))
```

### Computing Support

```{r}
